\section{Results and Discussion}

This prototype was successfully implemented to include all the functionalities mentioned in the Methodology for a single user, who can subscribe to a single currency type. However, this system could be extended to accommodate multiple users as well as to include the functionality for a single user to be able to subscribe to multiple currency types for notifications.\\

Since the exchange rates are available to Day-Traders on a daily basis only, and this application succeeds at providing exchange rate information at a higher frequency (hourly) even with a free API subscription plan, this could be seen as a useful service for Day-Traders. This could however be extended to provide data every 30 seconds with a paid subscription, or even to be updated every second with the same API.\\

There were several challenges encountered during the design and development of this application and one of which would be the implementation of a sleep mode for the NodeMCU. As the exchange rate information is required at high rates (30 seconds or less), it was not possible to implement a sleep mode energy saving algorithm for the NodeMCU and the constrained devices connected to it, at times when the Forex market is active.

\section{Conclusion}

Day Trading is an important activity to maintain the value of a currency type. The value of currency in the Forex market is determined by the supply and demand of currency and Day-trading supports this process. This project included the implementation of a prototype of a service to provide Day-Traders with exchange rate information and several Technical indicators over a period of time information which they require to conduct their Day-Trading activities successfully. The ability to view this information through live dashboards and to receive notifications regarding their investments automate the process of having to monitor the exchange rates manually.
